timesliced_random_cell_selection

### 2019-01-08 src/BACKUPtimesliced_random_cell_selection.Rmd

```{r}
background_all$temp_depth <- NA
background_all$temp_surface <- NA
background_all$salinity_depth <- NA
background_all$salinity_surface <- NA
background_all$chl_depth <- NA
background_all$chl_surface <- NA
background_all$o2_depth <- NA
background_all$o2_surface <- NA
background_all$mlp_surface <- NA
background_all$ssh_surface <- NA
```

Second you need to put the background (background_all) into a spatialpointsdataframe.
```{r}
background_all2 <- background_all[background_all$year == 2009, ]
xy <- background_all2[ ,c("longitude_meters","latitude_meters")] # This is to tell R where the coordinates are. Note that the column order needs to be longitude, latitude

@@

    }
}
write.csv(background_all_sp, "../output/bio/background_complete_2009.csv", row.names = FALSE)
background_all2 <- as.data.frame(background_all_sp)
head(background_all_sp)
```

@@

first rbind... (this you can delete if you had run the code at once)
```{r}
back1998 <- read.csv("../output/bio/background_complete_1998.csv", header = TRUE)
back1999 <- read.csv("../output/bio/background_complete_1999.csv", header = TRUE)
back2000_2003 <- read.csv("../output/bio/background_complete_2000_2003.csv", header = TRUE)
back2004_2006 <- read.csv("../output/bio/background_complete_2004_2006.csv", header = TRUE)
back2007_2011 <- read.csv("../output/bio/background_complete_2007_2011.csv", header = TRUE)
back2012_2016 <- read.csv("../output/bio/background_complete_2012_2016.csv", header = TRUE)

background_all <- rbind(back1998, back1999, back2000_2003, back2004_2006, back2007_2011, back2012_2016)
head(background_all)
```

@@

```{r}
backna <- sum(!complete.cases(background_all2)) #this just counts the number of rows that contain NA values
backna
background_all2 <- background_all2[complete.cases(background_all2), ] #removes NA values
backna2 <- sum(!complete.cases(background_all)) #this just counts the number of rows that contain NA values
backna2
write.csv(background_all, "../output/bio/background_complete_na.csv", row.names = FALSE)
```

randomly select 10000 rows from each timeslice
```{r}
#background_all <- read.csv("../output/bio/background_complete_na.csv", header = TRUE)
split_cell_back <- split(background_all, list(background_all$year, background_all$month), drop = TRUE)

no_timeslices <- length(split_cell_back) # how many levels (time slices) are in the list
bckoutput <- "../output/bio/background/rand20k/no_na/" #where the files are to be saved to
for (i in 1:no_timeslices){
  timeslice <- split_cell_back[[i]]
  timeslice <- as.data.frame(timeslice)
  write.csv(timeslice, paste0(bckoutput, names(lapply(split_cell_back, names))[i], ".csv"), row.names = FALSE) 
}
```

```{r}
bckrnd_folder <- "../output/bio/background/rand20k/no_na/"      # path to folder that holds multiple .csv files
bckrnd_list <- list.files(path = bckrnd_folder, pattern="*.csv") # create list of all .csv files in folder
randbckoutput <- "../output/bio/background/rand20k/no_na_10krand/" #where the files are to be saved to
# read in each .csv file in file_list and create a data frame with the same name as the .csv file
for (i in 1:length(bckrnd_list)){
  sel <- read.csv(paste(bckrnd_folder, bckrnd_list[i], sep=''))
  sel <- sample_n(sel, 10000) #where 10000 = number of rows to sample 
  write.csv(sel, file = paste0(randbckoutput, bckrnd_list[i]), row.names = FALSE) #dont need to add .csv as it's already in the filename
}
head(sel)
```

crap - the years from 2007 onwards have less than 10k points to choose from...
create a random 30k for each of these month/year periods

>>>>

```{r}
background_all <- read.csv("../output/bio/background_all_lonlat_nafo2_sciname_amo_nao_depthname_bath_cellobs.csv", header = TRUE)
background_all$temp_depth <- NA
background_all$temp_surface <- NA
background_all$salinity_depth <- NA
background_all$salinity_surface <- NA
background_all$chl_depth <- NA
background_all$chl_surface <- NA
background_all$o2_depth <- NA
background_all$o2_surface <- NA
background_all$mlp_surface <- NA
background_all$ssh_surface <- NA
```

Second you need to put the background (background_all) into a spatialpointsdataframe.
```{r}
background_all2 <- background_all[background_all$year == 1999 & background_all$month == 7, ]
xy <- background_all2[ ,c("longitude_meters","latitude_meters")] # This is to tell R where the coordinates are. Note that the column order needs to be longitude, latitude

@@

    }
}
write.csv(background_all_sp, "../output/bio/background_complete_1999.7.csv", row.names = FALSE)
background_all2 <- as.data.frame(background_all_sp)
head(background_all_sp)
```

@@

first rbind... (this you can delete if you had run the code at once)
```{r}
back1998 <- read.csv("../output/bio/background/correct_random_files/background_complete_1998.csv", header = TRUE)
back1999 <- read.csv("../output/bio/background/correct_random_files/background_complete_1999.csv", header = TRUE)
back2000 <- read.csv("../output/bio/background/correct_random_files/background_complete_2000.csv", header = TRUE)
back2001 <- read.csv("../output/bio/background/correct_random_files/background_complete_2001.csv", header = TRUE)
back2002 <- read.csv("../output/bio/background/correct_random_files/background_complete_2002.csv", header = TRUE)
back2003 <- read.csv("../output/bio/background/correct_random_files/background_complete_2003.csv", header = TRUE)
back2004 <- read.csv("../output/bio/background/correct_random_files/background_complete_2004.csv", header = TRUE)
back2005 <- read.csv("../output/bio/background/correct_random_files/background_complete_2005.csv", header = TRUE)
back2006 <- read.csv("../output/bio/background/correct_random_files/background_complete_2006.csv", header = TRUE)
back2007 <- read.csv("../output/bio/background_complete_2007.csv", header = TRUE)
back2008 <- read.csv("../output/bio/background_complete_2008.csv", header = TRUE)
back2009 <- read.csv("../output/bio/background_complete_2009.csv", header = TRUE)
back2010 <- read.csv("../output/bio/background_complete_2010.csv", header = TRUE)
back2011 <- read.csv("../output/bio/background_complete_2011.csv", header = TRUE)
back2012 <- read.csv("../output/bio/background_complete_2012.csv", header = TRUE)
back2013 <- read.csv("../output/bio/background_complete_2013v2.csv", header = TRUE)
back2014 <- read.csv("../output/bio/background_complete_2014.csv", header = TRUE)
back2015 <- read.csv("../output/bio/background_complete_2015.csv", header = TRUE)

background_all <- rbind(back1998, back1999, back2000, back2001, back2002, back2003, back2004, back2005, back2006, back2007, back2008, back2009, back2010, back2011, back2012, back2013, back2014, back2015)
head(background_all)
write.csv(background_all, "../output/bio/background_all_complete.csv", row.names = FALSE)
```

the prior files...

```{r}
#back1 <- read.csv("../output/bio/background/rand20k/no_na_10krand/1999.1.csv", header = TRUE)
#back2 <- read.csv("../output/bio/background/rand20k/no_na_10krand/1999.2.csv", header = TRUE)
back3 <- read.csv("../output/bio/background/rand20k/no_na_10krand/1999.3.csv", header = TRUE)
back4 <- read.csv("../output/bio/background/rand20k/no_na_10krand/1999.4.csv", header = TRUE)
back5 <- read.csv("../output/bio/background/rand20k/no_na_10krand/1999.5.csv", header = TRUE)
back6 <- read.csv("../output/bio/background/rand20k/no_na_10krand/1999.6.csv", header = TRUE)
back7 <- read.csv("../output/bio/background_complete_1999.7.csv", header = TRUE)
#back8 <- read.csv("../output/bio/background/rand20k/no_na_10krand/1999.8.csv", header = TRUE)
back9 <- read.csv("../output/bio/background/rand20k/no_na_10krand/1999.9.csv", header = TRUE)
back10 <- read.csv("../output/bio/background/rand20k/no_na_10krand/1999.10.csv", header = TRUE)
back11 <- read.csv("../output/bio/background/rand20k/no_na_10krand/1999.11.csv", header = TRUE)
back12 <- read.csv("../output/bio/background/rand20k/no_na_10krand/1999.12.csv", header = TRUE)

back1998 <- rbind(back3, back4, back5, back6, back7, back9, back10, back11, back12)
#back1998 <- rbind(back1, back2, back3, back4, back5, back6, back7, back8, back9, back10, back11, back12)
write.csv(back1998, "../output/bio/background/correct_random_files/background_complete_1999.csv", row.names = FALSE)
```

@@

```{r}
backna <- sum(!complete.cases(background_all)) #this just counts the number of rows that contain NA values
backna
```

XXX THIS NEEDS EDITING AND MOVING TOO XXXX
